### 2022-07-23 sections/bdt_Htautau.tex
updates plots labels

%Figure~\ref{fig:asimov_prefitbdt} show the postfits to the data of BDT observable in each SRs with all background processes constrained to the SM expectation.
%The level of discrimination between signal and background achieved by the BDTs is illustrated in Figure~\ref{fig:overtrain_hadhad}-~\ref{fig:overtrain_lhadhad}.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\input{\FCNCFigures/tex/BDTinput}
\begin{figure}[H]
\centering
\begin{tabular}{@{}ccc@{}}
%\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l2tau1bnj_os/tau_pt_0.pdf} &
%\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l1tau1b1j_ss_vetobtagwp70_highmet/tau_pt_0.pdf}&
%\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l1tau1b2j_ss_vetobtagwp70_highmet/tau_pt_0.pdf}\\
\includegraphics[page=1,width=0.28\textwidth]{figures/new_pt/log_or_nolog/tuH_reg1l2tau1bnj_os_log_.pdf} &
\includegraphics[page=1,width=0.28\textwidth]{figures/new_pt/log_or_nolog/tuH_reg1l1tau1b1j_ss_log_.pdf}&
\includegraphics[page=1,width=0.28\textwidth]{figures/new_pt/log_or_nolog/tuH_reg1l1tau1b2j_ss_log_.pdf}\\
(a) & (b) & (c) \\
%(a1) \pT(\tauhad) in $t_{\ell}\thadhad$ & (a2) \pT(\tauhad) in  $t_{\ell}\tauhad$-1j& (a3) \pT(\tauhad) in $t_{\ell}\tauhad$-2j\\
\includegraphics[page=1,width=0.28\textwidth]{figures/new_pt/log_or_nolog/tuH_reg1l1tau1b2j_os_log_.pdf}&
\includegraphics[page=1,width=0.28\textwidth]{figures/new_pt/log_or_nolog/tuH_reg1l1tau1b3j_os_log_.pdf} &
\includegraphics[page=1,width=0.28\textwidth]{figures/new_pt/log_or_nolog/tuH_reg1l2tau1bnj_ss_log_.pdf} \\
(d) & (e) & (f)\\
%(b1) \pT(\tauhad) in $t_h\tlhad$-2j & (b2) \pT(\tauhad) in  $t_h\tlhad$-3j & (b3) \pT(\tauhad) in $t_h\thadhad$-2j \\
\includegraphics[page=1,width=0.28\textwidth]{figures/new_pt/log_or_nolog/tuH_reg2mtau1b2jos_log_.pdf}&
\includegraphics[page=1,width=0.28\textwidth]{figures/new_pt/log_or_nolog/tuH_reg2mtau1b3jos_log_.pdf}&
\includegraphics[page=1,width=0.28\textwidth]{figures/new_pt/log_or_nolog/tuH_reg2mtau1b3jss_log_.pdf}\\
(g) & (h) & (i)\\
%(c1) \pT(\tauhad) in $t_h\thadhad$-3j\\
\end{tabular}
\caption{Leading $\thad$ $\pt$  distributions obtained before the fit to data (``Pre-Fit'') showing 
  the expected background and $tuH$ signals after applying fake factors in the following regions: $t_{\ell}\thadhad$ (a),
 $t_{\ell}\tauhad$-1j (b),  $t_{\ell}\tauhad$-2j (c), $t_h\tlhad$-2j (d), $t_h\tlhad$-3j (e), $t_{\ell}\thadhad$-SS  (f), $t_h\thadhad$-2j (g), $t_h\thadhad$-3j (h) and $t_h\thadhad$-3j SS (i).
 The total size of the statistical and systematic uncertainties of the background prediction is indicated by the hatched band.
 %The uncertainty band includes both the statistical and systematic uncertainties in the background prediction.
 Overflow events are included in the last bin. ``Other MC'' (``Rare'') includes single top, $V$+jets, and other small backgrounds in the leptonic (hadronic) channel. The $tuH$ signals are scaled using
 normalization factors of 2 to 50.   
%( only subtau real refers to $t\bar{t}$ MC with leading tau faked by other object, subleading tau from real contribution. 
The lower panels show the data to prediction ratio.}
\label{fig:taupt_prefit}
\end{figure}

@@

\begin{figure}[H]
\centering
\begin{tabular}{@{}ccc@{}}
%\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l2tau1bnj_os/tau_pt_0.pdf} &
%\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l1tau1b1j_ss_vetobtagwp70_highmet/tau_pt_0.pdf}&
%\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l1tau1b2j_ss_vetobtagwp70_highmet/tau_pt_0.pdf}\\
\includegraphics[page=1,width=0.28\textwidth]{figures/mtt/tuH_reg1l2tau1bnj_os_log_mtt.pdf} &
\includegraphics[page=1,width=0.28\textwidth]{figures/mtt/tuH_reg1l1tau1b1j_ss_log_mtt.pdf}&
\includegraphics[page=1,width=0.28\textwidth]{figures/mtt/tuH_reg1l1tau1b2j_ss_log_mtt.pdf}\\
(a) & (b) & (c) \\
%(a1) \pT(\tauhad) in $t_{\ell}\thadhad$ & (a2) \pT(\tauhad) in  $t_{\ell}\tauhad$-1j& (a3) \pT(\tauhad) in $t_{\ell}\tauhad$-2j\\
\includegraphics[page=1,width=0.28\textwidth]{figures/mtt/tuH_reg1l1tau1b2j_os_log_mtt.pdf}&
\includegraphics[page=1,width=0.28\textwidth]{figures/mtt/tuH_reg1l1tau1b3j_os_log_mtt.pdf}&
\includegraphics[page=1,width=0.28\textwidth]{figures/mtt/tuH_reg1l2tau1bnj_ss_log_mtt.pdf}\\
(d) & (e) & (f)\\
%(b1) \pT(\tauhad) in $t_h\tlhad$-2j & (b2) \pT(\tauhad) in  $t_h\tlhad$-3j & (b3) \pT(\tauhad) in $t_h\thadhad$-2j \\
\includegraphics[page=1,width=0.28\textwidth]{figures/mtt/tuH_reg2mtau1b2jos_log_mtt.pdf}&
\includegraphics[page=1,width=0.28\textwidth]{figures/mtt/tuH_reg2mtau1b3jos_log_mtt.pdf}&
\includegraphics[page=1,width=0.28\textwidth]{figures/mtt/tuH_reg2mtau1b3jss_log_mtt.pdf}\\
(g) & (h) & (i)\\
%(c1) \pT(\tauhad) in $t_h\thadhad$-3j\\
\end{tabular}
\caption{Visible invariant mass of the di-tau system ($m_{\tau\tau}$) distributions obtained before the fit to data (``Pre-Fit'') showing 
  the expected background and $tuH$ signals after applying fake factors in the following regions: $t_{\ell}\thadhad$ (a),
 $t_{\ell}\tauhad$-1j (b),  $t_{\ell}\tauhad$-2j (c), $t_h\tlhad$-2j (d), $t_h\tlhad$-3j (e), $t_{\ell}\thadhad$-SS (f), $t_h\thadhad$-2j (g), $t_h\thadhad$-3j (h) and $t_h\thadhad$-3j SS (i).
 The total size of the statistical and systematic uncertainties of the background prediction is indicated by the hatched band.
 %The uncertainty band includes both the statistical and systematic uncertainties in the background prediction.
 Overflow events are included in the last bin. ``Other MC'' (``Rare'') includes single top, and $V$+jets and other small backgrounds in the leptonic (hadronic) channel. The $tuH$ signal is scaled using a normalization factor of 2 to 50.   
%( only subtau real refers to $t\bar{t}$ MC with leading tau faked by other object, subleading tau from real contribution. 
The lower panels show the data to prediction ratio.}
\label{fig:mtt}
\end{figure}

>>>>

%Figure~\ref{fig:asimov_prefitbdt} show the postfits to the data of BDT observable in each SRs with all background processes constrained to the SM expectation.
%The level of discrimination between signal and background achieved by the BDTs is illustrated in Figure~\ref{fig:overtrain_hadhad}-~\ref{fig:overtrain_lhadhad}.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\input{\FCNCFigures/tex/BDTinput}
\begin{figure}[H]
\centering
\begin{tabular}{@{}ccc@{}}
%\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l2tau1bnj_os/tau_pt_0.pdf} &
%\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l1tau1b1j_ss_vetobtagwp70_highmet/tau_pt_0.pdf}&
%\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l1tau1b2j_ss_vetobtagwp70_highmet/tau_pt_0.pdf}\\
\includegraphics[page=1,width=0.28\textwidth]{figures/pt/tuH_reg1l2tau1bnj_os_log_.pdf} &
\includegraphics[page=1,width=0.28\textwidth]{figures/pt/tuH_reg1l1tau1b1j_ss_log_.pdf}&
\includegraphics[page=1,width=0.28\textwidth]{figures/pt/tuH_reg1l1tau1b2j_ss_log_.pdf}\\
(a) & (b) & (c) \\
%(a1) \pT(\tauhad) in $t_{\ell}\thadhad$ & (a2) \pT(\tauhad) in  $t_{\ell}\tauhad$-1j& (a3) \pT(\tauhad) in $t_{\ell}\tauhad$-2j\\
\includegraphics[page=1,width=0.28\textwidth]{figures/pt/tuH_reg1l1tau1b2j_os_log_.pdf}&
\includegraphics[page=1,width=0.28\textwidth]{figures/pt/tuH_reg1l1tau1b3j_os_log_.pdf} &
\includegraphics[page=1,width=0.28\textwidth]{figures/pt/tuH_reg1l2tau1bnj_ss_log_.pdf} \\
(d) & (e) & (f)\\
%(b1) \pT(\tauhad) in $t_h\tlhad$-2j & (b2) \pT(\tauhan 3j & (b3) \pT(\tauhad) in $t_h\thadhad$-2j \\
\includegraphics[page=1,width=0.28\textwidth]{figures/pt/tuH_reg2mtau1b2jos_log_.pdf}&
\includegraphics[page=1,width=0.28\textwidth]{figures/pt/tuH_reg2mtau1b3jos_log_.pdf}&
\includegraphics[page=1,width=0.28\textwidth]{figures/pt/tuH_reg2mtau1b3jss_log_.pdf}\\
(g) & (h) & (i)\\
%(c1) \pT(\tauhad) in $t_h\thadhad$-3j\\
\end{tabular}
\caption{Leading $\thad$ $\pt$  distributions obtained before the fit to data (``Pre-Fit'') showing 
  the expected background and $tuH$ signals after applying fake factors in the following regions: $t_{\ell}\thadhad$ (a),
 $t_{\ell}\tauhad$-1j (b),  $t_{\ell}\tauhad$-2j (c), $t_h\tlhad$-2j (d), $t_h\tlhad$-3j (e), $t_{\ell}\thadhad$-SS  (f), $t_h\thadhad$-2j (g), $t_h\thadhad$-3j (h) and $t_h\thadhad$-3j SS (i).
 The total size of the statistical and systematic uncertainties of the background prediction is indicated by the hatched band.
 %The uncertainty band includes both the statistical and systematic uncertainties in the background prediction.
 Overflow events are included in the last bin. ``Other MC'' includes single top, $V$+jets, and other small backgrounds in the leptonic and hadronic channels. The $tuH$ signals are scaled using
 normalization factors of 2 to 50.   
%( only subtau real refers to $t\bar{t}$ MC with leading tau faked by other object, subleading tau from real contribution. 
The lower panels show the data to prediction ratio.}
\label{fig:taupt_prefit}
\end{figure}

@@

\begin{figure}[H]
\centering
\begin{tabular}{@{}ccc@{}}
%\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l2tau1bnj_os/tau_pt_0.pdf} &
%\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l1tau1b1j_ss_vetobtagwp70_highmet/tau_pt_0.pdf}&
%\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l1tau1b2j_ss_vetobtagwp70_highmet/tau_pt_0.pdf}\\
\includegraphics[page=1,width=0.28\textwidth]{figures/mtt/tuH_reg1l2tau1bnj_os_log_mtt.pdf} &
\includegraphics[page=1,width=0.28\textwidth]{figures/mtt/tuH_reg1l1tau1b1j_ss_log_mtt.pdf}&
\includegraphics[page=1,width=0.28\textwidth]{figures/mtt/tuH_reg1l1tau1b2j_ss_log_mtt.pdf}\\
(a) & (b) & (c) \\
%(a1) \pT(\tauhad) in $t_{\ell}\thadhad$ & (a2) \pT(\tauhad) in  $t_{\ell}\tauhad$-1j& (a3) \pT(\tauhad) in $t_{\ell}\tauhad$-2j\\
\includegraphics[page=1,width=0.28\textwidth]{figures/mtt/tuH_reg1l1tau1b2j_os_log_mtt.pdf}&
\includegraphics[page=1,width=0.28\textwidth]{figures/mtt/tuH_reg1l1tau1b3j_os_log_mtt.pdf}&
\includegraphics[page=1,width=0.28\textwidth]{figures/mtt/tuH_reg1l2tau1bnj_ss_log_mtt.pdf}\\
(d) & (e) & (f)\\
%(b1) \pT(\tauhad) in $t_h\tlhad$-2j & (b2) \pT(\tauhad) in  $t_h\tlhad$-3j & (b3) \pT(\tauhad) in $t_h\thadhad$-2j \\
\includegraphics[page=1,width=0.28\textwidth]{figures/mtt/tuH_reg2mtau1b2jos_log_mtt.pdf}&
\includegraphics[page=1,width=0.28\textwidth]{figures/mtt/tuH_reg2mtau1b3jos_log_mtt.pdf}&
\includegraphics[page=1,width=0.28\textwidth]{figures/mtt/tuH_reg2mtau1b3jss_log_mtt.pdf}\\
(g) & (h) & (i)\\
%(c1) \pT(\tauhad) in $t_h\thadhad$-3j\\
\end{tabular}
\caption{Visible invariant mass of the di-tau system ($m_{\tau\tau}$) distributions obtained before the fit to data (``Pre-Fit'') showing 
  the expected background and $tuH$ signals after applying fake factors in the following regions: $t_{\ell}\thadhad$ (a),
 $t_{\ell}\tauhad$-1j (b),  $t_{\ell}\tauhad$-2j (c), $t_h\tlhad$-2j (d), $t_h\tlhad$-3j (e), $t_{\ell}\thadhad$-SS (f), $t_h\thadhad$-2j (g), $t_h\thadhad$-3j (h) and $t_h\thadhad$-3j SS (i).
 The total size of the statistical and systematic uncertainties of the background prediction is indicated by the hatched band.
 %The uncertainty band includes both the statistical and systematic uncertainties in the background prediction.
 Overflow events are included in the last bin. ``Other MC''  includes single top, and $V$+jets and other small backgrounds in the leptonic and hadronic channels. The $tuH$ signal is scaled using a normalization factor of 2 to 50.   
%( only subtau real refers to $t\bar{t}$ MC with leading tau faked by other object, subleading tau from real contribution. 
The lower panels show the data to prediction ratio.}
\label{fig:mtt}
\end{figure}

### 2022-07-23 sections/data_presel.tex
updates plots labels

%%%%%%%%%%%%%%%
\begin{table*}[t!]
\caption{\small{Summary of preselection requirements. 
The leading and subleading $\had$ candidates are denoted by $\tau_{\mathrm{had1}}$ and $\tau_{\mathrm{had2}}$ respectively.}}
\begin{center}
\begin{tabular}{c|ccc|c}
\toprule\toprule
\multirow{2}{*}{Requirement} &  \multicolumn{3}{c|}{leptonic channel}  & \multicolumn{1}{c}{hadronic channel} \\ 
%\multirow{2}{*}{Requirement} &  \multicolumn{3}{c|}{leptonic channel}  & hadronic channel \\ 
& $t_h\lephad$ & $t_{\ell}\hadhad$ &  $t_{\ell}\had$ & $t_h\hadhad$\\
\midrule
Trigger & \multicolumn{3}{c|}{single-lepton trigger} & di-$\tau$ trigger  \\
Leptons  & \multicolumn{3}{c|}{=1 isolated $e$ or $\mu$}  & =0 isolated $e$ or $\mu$ \\
$\had$  & $=$1 $\had$ & $\geq$2 $\had$ & $=$1 $\had$ & $\geq$2 $\had$ \\
Electric charge ($Q$) & $Q_\ell \times Q_{\tau_{\mathrm{had1}}} < 0$ & $Q_{\tau_{\mathrm{had1}}} \times Q_{\tau_{\mathrm{had2}}} < 0$ & $Q_\ell \times Q_{\tau_{\mathrm{had1}}} > 0$ & $Q_{\tau_{\mathrm{had1}}} \times Q_{\tau_{\mathrm{had2}}} < 0$ \\
Jets  &   $\geq$ 3 jets & $\geq$1 jets & $\geq$2 jets & $\geq$3 jets \\
$b$-tagging & \multicolumn{3}{c|}{=1 $b$-jets} & =1 $b$-jets\\
\bottomrule\bottomrule
\end{tabular}
\label{tab:preselection}
\end{center}
\end{table*}
%%%%%%%%%%%%%%%

>>>>

%%%%%%%%%%%%%%%
\begin{table*}[t!]
\caption{\small{Summary of preselection requirements. 
The leading and subleading $\had$ candidates are denoted by $\tau_{\mathrm{had1}}$ and $\tau_{\mathrm{had2}}$ respectively.}}
\begin{center}
\begin{tabular}{c|ccc|c}
\toprule\toprule
\multirow{2}{*}{Requirement} &  \multicolumn{3}{c|}{leptonic channel}  & \multicolumn{1}{c}{hadronic channel} \\ 
%\multirow{2}{*}{Requirement} &  \multicolumn{3}{c|}{leptonic channel}  & hadronic channel \\ 
& $t_h\lephad$ & $t_{\ell}\hadhad$ &  $t_{\ell}\had$ & $t_h\hadhad$\\
\midrule
Trigger & \multicolumn{3}{c|}{single-lepton trigger} & di-$\tau$ trigger  \\
Leptons  & \multicolumn{3}{c|}{=1 isolated $e$ or $\mu$}  & =0 isolated $e$ or $\mu$ \\
$\had$  & $=$1 $\had$ & $=$2 $\had$ & $=$1 $\had$ & $=$2 $\had$ \\
Electric charge ($Q$) & $Q_\ell \times Q_{\tau_{\mathrm{had1}}} < 0$ & $Q_{\tau_{\mathrm{had1}}} \times Q_{\tau_{\mathrm{had2}}} < 0$ & $Q_\ell \times Q_{\tau_{\mathrm{had1}}} > 0$ & $Q_{\tau_{\mathrm{had1}}} \times Q_{\tau_{\mathrm{had2}}} < 0$ \\
Jets  &   $\geq$ 3 jets & $\geq$1 jets & $\geq$2 jets & $\geq$3 jets \\
$b$-tagging & \multicolumn{3}{c|}{=1 $b$-jets} & =1 $b$-jets\\
\bottomrule\bottomrule
\end{tabular}
\label{tab:preselection}
\end{center}
\end{table*}
%%%%%%%%%%%%%%%
